Accessories dominate the costs of producing seed

### 2016-12-13 ms/Accessory/Wenk-Accessory-SI.Rnw
separating out supplementary material figures

@@

TableSXX <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)

names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
TableSXX[,3] <- format(TableSXX[,3],digits=2,nsmall=2)
TableSXX[,6] <- format(TableSXX[,6],digits=2,nsmall=2)
TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
TableSXX[,4] <- format_p(TableSXX[,4])
TableSXX[,7] <- format_p(TableSXX[,7])

TableSXX$species  <- paste("\\textit{",unique(TableSXX$species),"}", sep="")

print(xtable(TableSXX,
               hline.after=c(1),
               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
               sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = TRUE
        , size = "small"
        , floating = FALSE)
@

Table SXX.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".

>>>>

<<echo=FALSE,results='asis'>>=
headers <- as.data.frame(matrix(vector(), 3,4,
                dimnames=list(c(), c("A","B","C","D"))),
                stringsAsFactors=F)
headers[1,] <- c("","Proportion","Proportion","Proportion")
headers[2,] <- c("","pollen-attraction","provisioning","success")
headers[3,] <- c("","investment to","investment to","investment to")

print(xtable(headers,
             hline.after=c(-1),
             align='p{0.1cm}p{11.5cm}|p{3cm}|p{3cm}|p{3cm}'),
        sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = FALSE
        , size = "small"
        , floating = FALSE)             
@

make_table_species_values_for_allocation_seedsize_table <- function(file) {
  data <- select(file,species,embryo_endo_costs, scaled_seed_count,scaled_ovule_count,
                 scaled_pollen_attract_costs,choosiness2,prop_prepollen_success, prop_prepollen_discarded,
                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  data
}

TableS2 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])

names(TableS2) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")

for (i in 2:12) {
TableS2[,i] <- format(TableS2[,i],digits=3,nsmall=2)
}

TableS2$species  <- paste("\\textit{",unique(TableS2$species),"}", sep="")

print(xtable(TableS2,
               hline.after=c(1),
               align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
               caption="Species values for data plotted in Figure 2",
               sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = TRUE
        , size = "small"
        , floating = FALSE))
@
Table S2. Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.

@@

TableS3 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)

names(TableS3) <- c("species","n","r$^2$","p", "n","r$^2$","p")
TableS3[,2] <- format(TableS3[,2],digits=2,nsmall=2)
TableS3[,3] <- format(TableS3[,3],digits=2,nsmall=2)
TableS3[,6] <- format(TableS3[,6],digits=2,nsmall=2)
TableS3[,5] <- format(TableS3[,5],digits=2,nsmall=2)
TableS3[,4] <- format_p(TableS3[,4])
TableS3[,7] <- format_p(TableS3[,7])

TableS3$species  <- paste("\\textit{",unique(TableS3$species),"}", sep="")

print(xtable(TableS3,
               hline.after=c(1),
               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
               sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = TRUE
        , size = "small"
        , floating = FALSE)
@

Table S3.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".

\clearpage
#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
```{r}
xvar <- "repro_inv"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

xvar <- "total_weight_0"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

xvar <- "age"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
mtext(text="age (years)",side=1,line=2,outer=FALSE)
mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
legend_with_r2(results,"topleft")
```

Table S4. Shifts in accessory costs with shifts in age, plant size, or reproductive effort. 
\clearpage
